\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-06-18 doc/incertae_sedis.tex
Make section on naming a bit clearer by adding subsubsection headings.

However, in the \emph{incertae sedis} framework, it is possible for one name to
apply to multiple nodes. For example, in Figure \ref{fig:One-name-can}b, the
name $E$ can apply to nodes $x$ and $y$. Here the name $E$ corresponds to the split
$E1\,E2\,|\bullet F\,G$, leaving $H$ out of the definition since $H$ is \emph{incertae sedis}. 
The two nodes $x$
and $y$ display the splits $E1\,E2\,|\bullet F\,G\,H$ and $E1\,E2\,H|\bullet
F\,G$ respectively, and both
of these splits display the split $E1\,E2\,|\bullet F\,G$, so the name $E$ can apply to both
$x$ and $y$. 
This cannot happen when the rooted splits that correspond to a taxonomic name
    are generated without\emph{ incertae sedis} taxa except at
monotypic nodes.

@@

It is also possible for multiple names to apply to a single node. For example,
in Figure \ref{fig:Multiple-names-can}a, the taxon $M$ corresponds to the split
$L1\,L2\,K\,|\bullet\,J$, and its child taxon $L$ corresponds to the split $L1\,L2\,|\bullet\,Y$.
The edge leading to $M$ is consistent with the split for $L$, but the name $L$ is
applied to the node with the smallest include group.
However, in the
solution tree (Fig. \ref{fig:Multiple-names-can}b), there is is only node for
both names $M$ and $L$ to apply to.
This kind of situation arises when a taxon
becomes monotypic after its \emph{incertae sedis} children are placed elsewhere.
For such cases, we can address this synonymy by (i) selecting a taxon at the
node that is ancestral to all other taxa and (ii) moving this taxon to a
newly-introduced out-degree-1 parent.  For example, $M$ is moved to an
out-degree-1 parent in Fig. \ref{fig:Multiple-names-can}c.
We repeatedly perform
this procedure until no taxon at the node is the parent of all taxa.

>>>>

\subsubsection{One name, multiple nodes}
However, in the \emph{incertae sedis} framework, it is possible for one name to
apply to multiple nodes. For example, in Figure \ref{fig:One-name-can}b, the
name $E$ can apply to nodes $x$ and $y$. Here the name $E$ corresponds to the split
$E1\,E2\,|\bullet F\,G$, leaving $H$ out of the definition since $H$ is \emph{incertae sedis}. 
The two nodes $x$
and $y$ display the splits $E1\,E2\,|\bullet F\,G\,H$ and $E1\,E2\,H|\bullet
F\,G$ respectively, and both
of these splits display the split $E1\,E2\,|\bullet F\,G$, so the name $E$ can apply to both
$x$ and $y$. 
This cannot happen when the rooted splits that correspond to a taxonomic name
    are generated without\emph{ incertae sedis} taxa except at
monotypic nodes.

@@

\subsubsection{One node, multiple names}
It is also possible for multiple names to apply to a single node. For example,
in Figure \ref{fig:Multiple-names-can}a, the taxon $M$ corresponds to the split
$L1\,L2\,K\,|\bullet\,J$, and its child taxon $L$ corresponds to the split $L1\,L2\,|\bullet\,Y$.
The edge leading to $M$ is consistent with the split for $L$, but the name $L$ is
applied to the node with the smallest include group.
However, in the
solution tree (Fig. \ref{fig:Multiple-names-can}b), there is is only node for
both names $M$ and $L$ to apply to.
This kind of situation arises when a taxon
becomes monotypic after its \emph{incertae sedis} children are placed elsewhere.
For such cases, we can address this synonymy by (i) selecting a taxon at the
node that is ancestral to all other taxa and (ii) moving this taxon to a
newly-introduced out-degree-1 parent.  For example, $M$ is moved to an
out-degree-1 parent in Fig. \ref{fig:Multiple-names-can}c.
We repeatedly perform
this procedure until no taxon at the node is the parent of all taxa.
